---
title: "Homework 2"
author: "Daniel Acuna"
date: "September 30, 2015"
output: html_document
---

```{r, echo=FALSE}
library(gapminder)
str(gapminder)
install.packages('ggplot2')
library('ggplot2')
```

Plot 1

```{r}
ggplot(data = gapminder, aes(x = gdpPercap, y = lifeExp, 
                             colour = continent)) + 
  geom_point(aes(shape = continent))
```

Plot 2

```{r}
ggplot(data = gapminder, aes(x = log(gdpPercap), y = lifeExp,
                             colour = continent)) + 
  geom_point(aes(shape = continent))
```

Plot 3
```{r}
ggplot(data = gapminder, aes(x = log(gdpPercap), y = lifeExp,
                             colour = continent)) + 
  geom_point(aes(shape = continent)) +
  geom_smooth(method = lm,
              se = FALSE)
```
Ugh! Can't fit only one. It's fitting for each continent... 

Plot 4 
```{r}
h <- ggplot(data = gapminder, aes(x = lifeExp)) + 
  geom_density(aes(fill = continent))
h + facet_wrap(~year)
```


Part II
use dplyr to calculate summary statistics
the function subset() may be useful (not necessary, just letting you know 
of a handy function)

```{r, echo=FALSE}
library(dplyr)
```

Plot 6

```{r}
ggplot(data = gapminder, aes(x = lifeExp)) + 
  geom_density(aes(fill = continent, alpha = 0.1))
```

Plot 7
Plot the mean life expectancy on a density plot for Asia

I want to work with only Asia, so technically I'd have to do something like this
gapminder$continent == 'Asia'
Running this command will only provide me with a TRUE and FALSE matrix 
Now, I need to only graph the mean lifeExp in Asia.
Again, I should first filter Asia and then graph the values for the lifeExp.
Subset allows me to graph only what I'm interested in graphing

```{r}

ggplot(data = subset (gapminder, continent == 'Asia'), aes(x = lifeExp) +
         geom_density()
```